---
title: "WriteUp Linear Model"
author: "Adam Ayala"
date: "10/20/2024"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model 1 SIMS~ARM
### Scarttered Plot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

The scatter plot made shows a positive correlation. Looks like those who do more simulations will have more arm strength although a majority of people are in middle between the numbers 50 and 100.

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```
These results being positive prove there is a positive correlation and with the number being closer to 1 means that there is something may be going on between the simulation and arm strength.


### Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The graph has a R squared of 0.4706 being smaller than we like since the higher it is  better. But this does show a positive correlation with our positive R-squared value. 


### Create target

```{r}
target<-data.frame(ARM=90, GRIP=90)
```

### Predict Target Point
```{r}
predict(model.1,target,interval=c("prediction"))
```

The table shows that our predicted target plot is 0.8155096 but 95% of the time, we are going to have a value between -1.617843 and 3.248863

### Linear Fit
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```

The line does go through the middle going well with our predictions but the points are still scattered meaning it does show a positive correlation but there can be things that are better as seen with our low R-squared value and Residual standard error value of 1.226.

### Model 2 SIMS vs GRIP
### Scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

This graph shows a positive linear relationship. With most dots being closer together especially in the middle.

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

A good value of 0.6398458 is shown proving a positive correlation but slightly smaller than model 1's value. But still pretty similar which can be seen with the plots on the visual graph being pretty close to each other but still different.

### Inferential results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The residual standard error is 1.295 and R-squared is 0.4094. RST is still pretty small and the R-squared is still small and not much difference was made from the previous graph of SIMS vs ARM.

### Predict Target Point of Model 2

```{r}
predict(model.2,target,interval=c("prediction"))
```

Model 2 had a -0.71800633 for a predicted point between the numbers of -3.292089 and 1.856077. 
Model 1 had a positive predicted point of 0.8155096 being much higher and closer to 1. along with a range that fits toward the positive being the highest of 3.248863 compared to model 2's highest interval of 1.856077. Also comparing the R-squared of model 1's 

### Scartter plot with linear fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```

The line does go through the middle and does appear to be close to the corner of the screen. But there quite a bit of big outliers in this graph. 

## Model 3 SIMS~ARM+GRIP
### Numerical Results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

This value would also show a positive correlation even when comparing the two types of data of ARM and GRIP. Because this value is closer to 1 than Model 1's and Model 2's number means this one is definitely better. Model 1's number is 0.6860073 and Model 2's nummber is 0.6398458 being smaller by almost .1 to Model 3. 

### Inferential Results Model 3

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

Our equation is SIMS = 0.037311ARM +  0.024470GRIP + -5.433871. With this we now have our equation of the line for a 3 dimensional graph.


