---
title: "WriteUp Linear Model"
author: "Adam Ayala"
date: "10/20/2024"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model 1 SIMS~ARM
### Scarttered Plot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

The scatter plot made shows a positive correlation. Looks like those who do more simulations will have more arm strength although a majority of people are in middle between the numbers 50 and 100.

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```
These results being positive prove there is a positive correlation and with the number being closer to 1 means that there is something may be going on between the simulation and arm strength.


### Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The graph has a R squared of 0.4706 being smaller than we like since the higher it is  better. But this does show a positive correlation with our positive R-squared value. 

### Linear Fit
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```

The line does go through the middle going well with our predictions but the points are still scattered meaning it does show a positive correlation but there can be things that are better as seen with our low R-squared value and Residual standard error value of 1.226.


### Create target

```{r}
target<-data.frame(ARM=90, GRIP=90)
```

### Predict Target Point
```{r}
predict(model.1,target,interval=c("prediction"))
```

The table shows that our predicted target plot is 0.8155096 but 95% of the time, we are going to have a value between -1.617843 and 3.248863

### Model 2 SIMS vs GRIP
### Scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

This graph shows a positive linear relationship. With most dots being closer together especially in the middle.

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

A good value of 0.6398458 is shown proving a positive correlation and the smaller it is the better. Which can be seen with the plots on th visual graph being pretty close.